Results

### 2024-10-02 scripts/Results.Rmd
mod

  theme(
    panel.background = element_rect(fill='transparent'), #transparent panel bg
    plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
    panel.grid.major = element_blank(), #remove major gridlines
    panel.grid.minor = element_blank(), #remove minor gridlines
    legend.background = element_rect(fill='transparent'), #transparent legend bg
    legend.box.background = element_rect(fill='transparent'), #transparent legend panel
    text = element_text(colour = "white")
  )

@@

>>>>

  theme(
    axis.text = element_text(color = 'white'),
    axis.ticks = element_line(color = 'white'),
    panel.background = element_rect(fill='transparent'), #transparent panel bg
    plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
    panel.grid.major = element_blank(), #remove major gridlines
    panel.grid.minor = element_blank(), #remove minor gridlines
    legend.background = element_rect(fill='transparent'), #transparent legend bg
    legend.box.background = element_rect(fill='transparent'), #transparent legend panel
    text = element_text(colour = "white")
  )

@@

5) Where were the populations found relative to the patch numbers?

patches <- read.csv('../data/SOS/PatchesPctChange.csv')

# showcase the area and proportion of patches
melted_patches <- select(patches, Rank, meanP, meanA, n_prop) |>
  pivot_longer(names_to = 'Metric', values_to = 'Value', cols = -Rank) |>
  mutate(Metric = case_when(
    Metric == 'meanA' ~ 'Mean Area', 
    Metric == 'meanP' ~ 'Mean Number',
    Metric == 'n_prop' ~ 'Occurrences'
  ))

cols <- c('Occurrences' = '#d95f02', 'Mean Area' = '#093824', 'Mean Number' =  '#7570b3')
shapes <- c('Occurrences' = 21, 'Mean Area' = 22, 'Mean Number' =  23)

patch_pts <- ggplot(data = melted_patches, 
                 aes(y = Rank, x = Value, fill = Metric, shape = Metric)) + 
  geom_jitter(height = 0.1, size = 4) +  
  theme_classic() + 
  scale_y_reverse(breaks = 1:9) + 
  scale_fill_manual(values = cols) + 
  scale_shape_manual(values = shapes) + 
  labs(
    x = 'Proportion', 
    y = 'Patch Rank', 
    title = 'Relationship between
    patches across landscape
    and new occurrences'
    ) + 
  theme(
    axis.text = element_text(color = 'white'),
    axis.ticks = element_line(color = 'white'),
    text = element_text(color = 'white'),
    aspect.ratio = 16/9,
    plot.title = element_text(hjust = 0.5), 
    legend.title = element_text(hjust = 0.5),
    legend.position = c(0.825, 0.2), 
    panel.background = element_rect(fill='transparent'), 
    plot.background = element_rect(fill='transparent', color=NA), 
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(), 
    legend.background = element_rect(fill='transparent'),
    legend.box.background = element_rect(fill='transparent') 
    )

ggsave('../plots/Ranks.png', patch_pts)
```

```{r}
melted_metrics <- select(patches, Rank, A_pct_change, P_pct_change) |>
  pivot_longer(names_to = 'Metric', values_to = 'Value', cols = -Rank) |>
  mutate(y = rep(1:2, times = 7))

ggplot(data = melted_patches, aes(x = Rank, y = y, fill = Value)) + 
  geom_tile() + 
  scale_fill_gradient2( 
    'Percent\nChange', 
    low = 'red', high = 'darkgreen', 
    breaks = seq(-100, 400, by = 100), limits = c(-100, 410),
    labels = paste0(seq(-100, 400, by = 100), '%')) + 
  scale_y_continuous(breaks=c(1, 2),
        labels=c("Area", "No. Patches")) + 
  theme_void()

rm(cols, shapes, melted_patches)
```
